\documentclass[11pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{geometry}
\geometry{margin=1in}

\title{The Inverse Hyperoperator Information Conjecture}
\author{Thomas Bradley}
\date{\today}

\begin{document}
\maketitle

\section{Conjecture}

Let $f$ be a holomorphic operator whose inverse requires $r$ independent
branch parameters $(b_1,\dots,b_r)\in\mathbb{Z}^r$ under analytic
continuation. We call $r$ the \emph{branch rank}.

\medskip
\noindent\textbf{Conjecture.}\;
Any globally continuous single-valued representation of the full inverse
of $f$ requires at least $r$ extra real coordinates beyond the base value
coordinates. Over $\mathbb{C}$ this gives
$\dim_{\mathbb{R}} \geq 2 + r$.

\section{First Prediction: Inverse of $z^z$}

The map $w = z^z = e^{z\log z}$ has two independent sources of
multivaluedness in its inverse: a logarithm branch $k\in\mathbb{Z}$
and a Lambert-$W$ branch $m\in\mathbb{Z}$. Hence $r=2$ and the
conjecture predicts $\dim_{\mathbb{R}} \geq 4$.

The only 4-real-dimensional normed division algebra is~$\mathbb{H}$.

\section{The Dimensional Ladder}

Each level of the hyperoperator hierarchy, when inverted, has
historically forced an extension of the number system. The conjecture
frames this as a single pattern:

\[
\mathbb{N}
  \xrightarrow{\;\text{inv.\ addition}\;}
\mathbb{Z}
  \xrightarrow{\;\text{inv.\ mult.}\;}
\mathbb{Q}
  \hookrightarrow \mathbb{R}
  \xrightarrow{\;\text{inv.\ exp.}\;}
\mathbb{C}
  \xrightarrow{\;\text{inv.\ }z^z\;}
\mathbb{H}\;?
\]

\begin{center}
\begin{tabular}{lcccc}
\toprule
Level & Inverse of & Type & Extra coords & Result \\
\midrule
1 & addition        & algebraic & sign             & $\mathbb{Z}$ \\
2 & multiplication  & algebraic & denominators     & $\mathbb{Q}\hookrightarrow\mathbb{R}$ \\
3 & exponentiation  & monodromy ($r\!=\!1$) & phase  & $\mathbb{C}$ \\
4 & $z^z$ / tetration & monodromy ($r\!=\!2$) & 2 branch indices & $\mathbb{H}\;?$ \\
\bottomrule
\end{tabular}
\end{center}

Levels 1--2 are algebraic closures under discrete inverse operations
(sign, denominators), not monodromy. The branch-rank formalism applies
precisely from level~3 onward, where analytic continuation is
meaningful. But the broader pattern is the same throughout: inverting
the $n$-th hyperoperator forces information that the current number
system cannot store, requiring a higher-dimensional extension.

\subsection*{Why normed division algebras?}

By the Hurwitz theorem (1898), the only finite-dimensional normed
division algebras over $\mathbb{R}$ are $\mathbb{R},\mathbb{C},
\mathbb{H},\mathbb{O}$ (dimensions $1,2,4,8$). There are many
4-dimensional real algebras, but only $\mathbb{H}$ is a normed
division algebra. The stronger form of the conjecture predicts each
extension lands on the next Hurwitz algebra specifically --- not just
any space of the right dimension.

\section{Two Forms of the Conjecture}

\begin{itemize}
\item \textbf{General:} branch rank $r$ forces $r$ extra real coordinates.
\item \textbf{Structural (stronger):} the extensions reproduce the normed
      division algebra sequence
      $\mathbb{R}\to\mathbb{C}\to\mathbb{H}$, with the algebra
      structure forced by monodromy.
\end{itemize}

Computational evidence for the $r=2$ prediction is in the
\texttt{computational-gap-detection/} folder. No formal proof is claimed.

\end{document}
